DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems

### 2012-11-26 Paper_May_2012/main.tex
Antwort auf Winnis letzte Aenderung

\subsubsection{\texttt{localfunc.h}}
The implementation of the boundary-functional $J$ follows the outline of the
computation of the cell-residual in \texttt{localpde.h}. 
\todo{Habe ich mal umgeschrieben, bitte nochmal ansehen~WW.}
The main difference, and common to all functionals is that we only 
want to evaluate a functional, i.e., calculate a single number, and not a
residual-vector\todocg{, i.e., calculate the elements of a vector Diesen Teil wuerde ich streichen.}. Thus, we 
just loop over the quadrature points and not over the degrees of freedom 
on the face. In the present situation, we want to evaluate a functional 
that consists of a boundary integral. Thus we need to evaluate 
integrals on faces, that lie on $\Gamma_{circ}$, instead of integrals over
elements. 
This face contributions are calculated in \texttt{BoundaryValue} and added to 
sum up to the value of $J$.

>>>>

\subsubsection{\texttt{localfunc.h}}
The implementation of the boundary-functional $J$ follows the outline of the
computation of the cell-residual in \texttt{localpde.h}. 
\todo{Habe ich mal umgeschrieben, bitte nochmal ansehen~WW.}
The main difference, and common to all functionals is that we only want to
\todocg{ evaluate a functional, i.e., <-wuerde ich streichen} calculate a single number, and not a
residual-vector\todocg{, i.e., calculate the elements of a vector Diesen Teil wuerde ich streichen.}. Thus, we 
just loop over the quadrature points and not over the degrees of freedom 
on the face. In the present situation, we want to evaluate a functional 
that consists of a boundary integral. Thus we need to evaluate 
integrals on faces, that lie on $\Gamma_{circ}$, instead of integrals over
elements. 
This face contributions are calculated in \texttt{BoundaryValue} and added to 
sum up to the value of $J$.
